---
title: "ps_4.Rmd"
author: "Hamaad Mehal"
date: "3/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(ggplot2)
library(tidycensus)
library(gt)


hhincome <- get_acs(geography = "county", variables = "B19013_001",
              key = "2eb808ca0dc4c89234af7d9380aab02d1bdccb4b", 
              year = 2018, geometry = TRUE)


# In this code chunk I loaded all of the necessary libraries, inputted the API
# key that I needed and used get_acs to pull the necessary information needed 
# for the madlibs

```

# Mad Libs

```{r, echo=FALSE}
sd_plus_one <- function(var, na.rm = TRUE){
  x<- sd(var, na.rm = na.rm + 1)
  return(x)
}

sdpo <- sd_plus_one(var = hhincome$estimate)

# This question just required an easy closing of parentheses which I was able 
# to do as I got the error message which indicated to me which parentheses 
# needed to be closed. 

```
The standard deviation of median income, plus one, is `r sdpo`.

```{r, echo=FALSE}
get_state <- function(countystate){
  countystate %>%
  str_split_fixed(.,", ", 2) %>% 
  pluck(2) %>% 
  return()
 }

got_state <- get_state(countystate = "Treasure County, Montana")

# Setting the input for get_state as countystate was necessary as the initial
# value was not being recognized. I made this a new function as I didn't want
# to return the name in my HTML. I also recognized that another issue was the
# fact that there was no pipe after countystate which I overlooked for a while 
# but was able to realize afterward.

```
Treasure County, Montana is located in the state of `r got_state`.

```{r, echo=FALSE}
upper_bound <- function(geoid){
 hhincome %>% 
 filter(GEOID == geoid) %>% 
 mutate(estimate + moe) %>% 
 pull()
}

upper_ECA <- upper_bound(geoid = "01005")

# This function uses the geoid as an input to get a given county and grab its 
# median income. The way I fixed it was by inserting geoid for the function(x)
# as this was what was causing the function to crash.

```
The upper bound for median income in Etowah County, Alabama (geoid = “01055”) is `r upper_ECA`.

# Question 2

``` {r Question2, echo = FALSE}
cali_hhincome <- get_acs(geography = "county", 
                  variables = "B19013_001", 
                  key = "86ce3e5f84f328bd7777fb5f4f55b8b836b45022", 
                  year = 2018, 
                  state = "California",
                  geometry = TRUE)
  
california_graph <- cali_hhincome %>% 
  ggplot(aes(fill = estimate)) + 
  geom_sf() + 
  scale_fill_viridis_c(option = "plasma",
                       direction = -1) + 
  labs(title = "Median Income by County in California",
       caption = "Source: American Communities Survey 2018",
       fill = "Median Income") +
  theme_void()

california_graph
# I specificied California when calling data to specifically pull from the state/
# After doing so, making the graph was easy as it relied on my just formatting 
# that information correctly, which I have done. 

```

# Question 3

The necessary information for this is in the ps_4_rpub.Rmd that I have 
also committed. This is the link:
https://rpubs.com/hamaadwmehal/582059

# Question 4
This powerpoint lacks information. Tax information isn't presented in an 
informative. It focuses on many elements tax code in a convoluted manner,
so the explanations prove weak for readers. This skips the nuances of tax 
code and does not provide context to readers that allows them to understand
the situation. The bullet points create their own stories that make an 
incoherent presentation. The attempts at logic are not subtantial from substance-
driven perspective and works in a very biased way. There is a whole lack of 
substance because of a pursuit to make graphs look good.. This data does not
truly explaing the tax system of California, and it doesn't argue for the validity
of California's tax structure. Since the information and the arguments don't seem to 
overlap much, the data contributes little to an argument in favor of California's tax
system which makes the visualizations somewhat obsolete. This data is not novel
for those who know the tax system but doesn't provide any information to those 
unfamiliar with it, making it a net negative all around.

# 5A
```{r, Question 5A, echo=FALSE}
get_dice <- function(n) {
  min(sample(letters, n, replace = TRUE))
}

dices <- get_dice(3)
print(dices)

```

# 5B
```{r, Question 5B, echo = FALSE}
roll_alpha_dice <- function(n) {
  map_chr(rep(1, n), ~ get_dice(3))
}

roll_alpha_dice(3)
```

# 5C
```{r, Question 5C, echo = FALSE}

tf <- function(n) {
  map(rep(4,n), ~ roll_alpha_dice(.x))
}

x <- tibble(throws = tf(100)) 

gt_table <- x %>%
  slice(1:5) %>%
  gt()
gt_table

vowels <- x %>%
  mutate(vowel = map_lgl(throws, ~ ifelse(.[[1]] %in% 
          c("a", "e", "i", "o", "u"), TRUE, FALSE)))

```
```{r, echo = FALSE}
inital <- vowels %>%
  count(vowel == TRUE)

count_initial <- sum(vowels$vowel)
```
`r count_initial` vowels

# 5D
```{r, Question 5D, echo = FALSE}
y <- tibble(throws = map(rep(4,1000), roll_alpha_dice)) %>%
  mutate(all_vowels = map_lgl(throws, ~ ifelse(all(. %in% c("a", "e", "i", "o", "u")), TRUE, FALSE)))

y_prob <- y %>%
  pull(all_vowels) %>%
  mean()
```
`r y_prob`. This is a significantly small number. 

# 5E
```{r, Question 5E, echo = FALSE}
first_roll <- function(n) {
  map(rep(1,n), ~ roll_alpha_dice(.x))
}

tibbledices <- tibble(throws = first_roll(1000)) %>% 
  unnest(throws)

tibbledices %>% 
  ggplot(aes(x = throws)) + 
  geom_bar() +
  xlab("Letters") + 
  ylab("Frequency")

```

# 5F
```{r, echo = FALSE}
new_roll <- function(n) {
  map_chr(rep(1,n), ~ get_dice(5))
}

new_roll2 <- tibble(throws = new_roll(1000)) %>% 
  unnest(throws)

combined <- bind_rows(tibbledices, new_roll2, .id = "id") %>% 
  mutate(id = case_when(id == 1 ~ "Three Dice",
                        id == 2 ~ "Five Dice"))

ggplot(combined, aes(x = throws)) + 
  geom_bar() +
  facet_wrap(~ id) +
  xlab("Letters") + 
  ylab("Frequency") +
  theme_classic()
```

Collaborators: Ibraheem Khan, Asmer Safi, Jun Yung Kim