---
title: "ps_7.Rmd"
author: "Hamaad Mehal"
date: "4/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(tidyverse)
library(janitor)
library(ggplot2)
library(tidycensus)
library(gt)
library(magrittr)
library(infer)
library(skimr)
library(tidyr)
library(broom)

data <- read.csv("data/HSall_members.csv")
```

# Question 1A
```{r Question 1A, echo=FALSE}
current_congress <- data %>%
  filter(congress == 116)  %>%
  filter(party_code != 328) %>%
  mutate(party_code, Party = ifelse(party_code == 100, "Democrat", "Republican")) %>%
  mutate(age = 2019 - born) %>%
  mutate(nominate_percentile = percent_rank(nominate_dim1) * 100, 0)
  
current_congress %>%
  skim(c(age,nominate_percentile))

# The process for this code was straightforward. Initially, I filtered for the
# 116th congress, and I filtered out independents (as was said in the 
# instructions). I then set all those who had a party_code of 100 to Democrat
# while giving those without that code the Republican label. I calculated age
# and percentile based on dimension 1 (liberal vs. conservative). Lastly, I
# skimmed the age and nominate_percentile as was required of the pset. This 
# a pretty straightforward process as I was told what to filter out, which
# variables to create (and along what lines), and to skim. My initial mistake
# was forgetting to filter out independents which initially skewed my results
# (e.g. Bernie Sanders was a Republican). This set me up for the rest of the
# PSET.

```

# Question 1B

```{r Question 1b, echo=FALSE}
ggplot(current_congress, aes(x = age, color = Party)) +
  geom_histogram(bins = 35) +
  theme_classic() +
  labs(
    x = "Age",
    y = "Number of Congress Members",
    title = "Ages of Members of the Current Congress (2019)",
    color = "Party"
  ) +
  scale_color_manual(values = c("blue", "red")) 


ggplot(current_congress, aes(x = nominate_percentile, color = Party)) +
  geom_histogram(bins = 35) +
  theme_classic() +
  labs(
    x = "Nominate Percentile",
    y = "Number of Congress Members",
    title = "Nominate Percentile of Members of the Current Congress (2019)",
    color = "Party"
  ) +
  scale_color_manual(values = c("blue", "red")) 
  

# The process of creating this was the easiest as I just had to create graphs
# for the variables I had created while being able to make the graphs however
# I wanted to. I did so by using the parties as points of comparison.

```

# Question 1C

```{r Question 1c, echo=FALSE}
see <- current_congress %>% 
  summarize(correlation = cor(age, nominate_percentile))

# I was able to do this by just using the correlation function which we learned
# in chapter 11 and practiced in class many times.

```
`r see`

A negative coefficient would mean the two variables are inversely related (as one variable increases, the second decreases, so in this case, as age increases, the nominate percentile decreases) whereas a positive coefficient would mean the two variable are directly related (as one variable increases, the second increases too, so in this case, as age increases, the nominate percentile increases).

# Question 1D

```{r Question 1d, echo=FALSE}
 current_congress %>%
  ggplot(aes(x=age, y = nominate_percentile, color = Party)) +
    geom_point() +
    geom_smooth(method = "glm", se = FALSE) +
    labs(x = "Age", y = "Percentile Rank (DW Nominate)", 
    title = "Relationship Between Age and DW Nominate Percentile",
    subtitle = "Higher scores represent more conservative positions") +
    scale_color_manual(values = c("blue","red")) +
    geom_smooth(method = "glm", se = FALSE, aes(group = 1), color = "black") +
    theme_classic() 

# The process of making this code was smooth as we were told to use geom_smooth
# and had practiced doing so in class. The only issue I encountered was how to 
# do the blackline which Ibraheem Khan helped me add to the graph.
    
```

The direction of the line _does_ match the sign of my correlation coefficient.

# Question 2A

```{r Question 2A, echo=FALSE}
democratic_members <- current_congress %>%
    filter(Party == "Democrat")

regression_model <- lm(nominate_percentile ~ age, data = democratic_members) %>%
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high)

regression_model %>%
  gt() %>%
  tab_header(title = "Effect of Age on DW Nominate Percentile") %>%
  tab_spanner(label = "Higher percentile suggests more conservative", columns = 
                c("term", "estimate", "conf.low", "conf.high")) %>%
  cols_label(term = "Variable", estimate = "Estimate", conf.low =
               "Lower Bound", conf.high = "Upper Bound")

# I initially filter for only democrats in the current congressional session (
# as was stipulated by the PSET rubric). I then ran a linear regression using 
# identical code to what we did in class last Thursday while just selecting for
# the terms we were told to. I then used the gt() function to make a table. 
# This question wasn't too difficult as the pset rubric told us what to do, and
# we had practiced doing something similar in class before. The only issue I
# had was with the tab_spanner labels, but I was able to figure that out quickly
# too. This helped me realize that I needed to filter out independents as my 
# stats were off from those on the rubric.

```

# Question 2B

```{r Question 2B, echo=FALSE}

# I was able to answer this question by reading chapter 11 and referring back
# to the Rubin Causal Model. 

```

The average treatment effect is -0.3322965 as that is the effect age has on 
the DW Nominate Percentile. This is the case as that number is the slope of 
the regression line, the metric for average treatment effect. I would say being
one year older lowers the democratic member of congress’s expected percentile 
rank for DW nominate scores by 0.3322965. We should not necessarily interpret 
the estimated correlation as causal because this is a mere observation. We 
could not experimentally manipulate any variables to try to understand if there
are any underlying causation factors in the data. Older democratic senators 
might be less conservative due to incumbency factors that allow them to be more
liberal due to their (potential) long standing in the party. We calculate a 
confidence interval around our average treatment effect to demonstrate the range
of possible values for the average treatment effect as our average treatment 
effect is just an estimate with degrees of uncertainty around its accuracy.

# Question 2C

```{r Question 2C, echo=FALSE}

# As on the previous question, I was able to answer this question by reading 
# chapter 11 and referring back to the Rubin Causal Model. 

```

The coefficient on military would be the average treatment effect that being
randomly assigned to the military has on DW nominate percentiles. However,
we are not able to observe differences in potential outcomes as, per the
Rubin Causal Model, we can only observe one observation at a time, a limit of
this model. However, we can say this analysis is causal due to the random
assignment of individuals to the treatment or control groups.

# Question 3

```{r Question 3, echo=FALSE}

question_3 <- data %>%
  filter(party_code == 100) %>%
  filter(chamber == "House" | chamber == "Senate") %>%
  mutate(age = 1789 + (congress-1) * 2 - born) %>%
  mutate(nominate_percentile = percent_rank(nominate_dim1) * 100, 0) %>%
  group_by(congress) %>%
  nest()

question_3_gg <- question_3 %>%
  mutate(mod = map(data, ~lm(nominate_percentile ~ age, data = .)), 
         reg_results = map(mod, ~ tidy(., conf.int = TRUE)),
         coef = map_dbl(reg_results, ~filter(., term == "age") %>%
         pull(estimate)), se = map_dbl(reg_results, ~ filter(.,
         term == "age") %>% pull(std.error)), upper = map_dbl
         (reg_results, ~filter(., term == "age") %>% pull(conf.high)),
         lower = map_dbl(reg_results, ~filter(., term == "age") %>% 
         pull(conf.low)))

ggplot(question_3_gg, aes(x = congress, y = coef)) +
  geom_point(color = "blue") +
  geom_errorbar(aes(x = congress, ymin = lower, ymax = upper), color = "blue") +
  theme_classic() +
  labs(title = "Average Treatment Effect of Age on Conservatism \n Among Democrats Over Time",
  subtitle = "Scores use DW Nominate Dimension 1 \n 95% Confidence Interval",
  x = "Congress", y = "Estimate")

# This question was by far the hardest and most time-consuming on the PSET. I
# was able to prepare the dataset correctly, but I realized I had to filter by 
# chamber later on as some data points weren't in either chamber (e.g. George 
# Washington, the President). When it came to creating new columns from the
# regression results, I began to have trouble. I received help from Jun Yong
# Kim on reg_results as I was getting an error for forgetting set the data
# argument. He also helped me on coef by reminding me to pull, which allowed me
# to figure out creating the rest of the columns. Finally, creating the graph
# was the easiest process as the most difficult part of it, geom_errorbar, was
# given which streamlined the creation process. Overall, I enjoyed this question
# the most as it taught me new things to use (geom_errorbar) while also creating,
# in my opinion, the best graph of the PSET.

```

Collaborators: Ibraheem Khan, Jun Yong Kim