---
title: "ps_8.Rmd"
author: "Hamaad Mehal"
date: "4/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(tidyverse)
library(janitor)
library(ggplot2)
library(tidycensus)
library(gt)
library(magrittr)
library(infer)
library(skimr)
library(tidyr)
library(broom)
library(fivethirtyeight)


data <- load("raw-data/tweetsnew.Rdata")
poll <- view(trump_approval_poll)
```

# 1A

```{r Question 1A, echo = FALSE}
tt <- tweets %>%
  group_by(week) %>%
  count(week) %>%
  rename(total_tweets = n)

# With this I created a new variable as was specified by the PSET's rubric.
# The code for this was pretty straightforward as I was told how to do it.

poll$week <- ceiling(as.numeric(difftime(poll$end_date, "2017-01-01", units = "days"))/7)

# I copied this from the rubric to create a "week" variable.

joined_polls <- poll %>%
  left_join(tt, by = "week")

# I left joined the poll with total_tweets as was specified in the instructions.
# This was just a little bit more difficult as it combined the data on week.

joined_polls[is.na(joined_polls)] <- 0

# I used https://stackoverflow.com/questions/10139284/set-na-to-0-in-r to help
# set the weeks in which there are no tweets to zero.

skim(joined_polls, total_tweets, approve)
```

# 1B

```{r Question 1B, echo = FALSE}
joined_polls$grade <- fct_explicit_na(joined_polls$grade, na_level = "(Missing)")

# We set the NAs in the data to missing as was specified by the rubric. This 
# was also hinted at in the pset rubric.

ggplot(joined_polls, aes(x = total_tweets, y = approve, color = grade)) +
  geom_point() +
  labs(x = "Total Tweets",
       y = "Approval Rating",
       title = "Trump Approval Ratings and Number of Tweets",
       subtitle = "Data from fivethirtyeight and Trump Twitter Archive") +
  theme_classic()

# I made the ggplot according to that in the infographic. Funny enough, I was
# having trouble with color before eventually realizing that I wasn't doing it
# according to grades. 

cor_jp <- joined_polls %>%
  summarise(correlation = cor(total_tweets, approve)) %>%
  pull(correlation)

# I found the correlation between tweets and the approval rating as was also
# specified by the rubric.

```


The correlation coefficient between the approval rating and the number of 
tweets is `r cor_jp`.


# 2A

```{r Question 2A, echo = FALSE}
joined_polls <- joined_polls %>%
  mutate(high_q = ifelse(joined_polls$grade == c("A+", "A", "A-"), 1, 0))

# I created a higher quality variable using code from the last pset and hints
# from the rubric.

regression_model <- lm(approve ~ total_tweets + high_q, data = joined_polls) 

# I ran a linear regression on total tweets and high q to establish a 
# relationship for the GT. 

gt_1 <- regression_model %>%
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high)

# Tidy'd the data and selected relevant data on it.

gt_1 %>%
  gt() %>%
  tab_header(title = "Effect of Number of Tweets and Poll Quality on Reported Approval Rating") %>%
  tab_spanner(label = "Data from fivethirtyeight and Trump Tweet Archive", columns = 
                c("term", "estimate", "conf.low", "conf.high")) %>%
  cols_label(term = "Variable", estimate = "Estimate", conf.low =
               "Lower Bound", conf.high = "Upper Bound")

# Used identical gt code as was on the last pset to make this table.

```

# 2B

The average treatment effect of high_q is that for high-quality polls, there 
is a 2.540 unit decrease in reported approval rating compared to all polls on 
all tweets. Trump's approval rating is predicted to be 2.3540 units lower than
that of all tweets (-0.004) when compared to its impact on high-quality polls. 
95% of the time, the true value is in between the bounds according to the 
frequentist interprtation. According to the Bayesian interpretation, we can be
95% sure that the true value will lie between the upper and lower bounds. 

# 2C

```{r Question 2C, echo = FALSE}
regression_model_2c <- lm(approve ~ total_tweets * high_q, data = joined_polls) 

# Received help from Jun Yong Kim on finding the effect of tweets on the high
# quality polls.

gt_r2c <- regression_model_2c %>%
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high)

# Used the same code as above for this and the gt. This process was easy as I
# copied the code from above for this.

gt_r2c %>%
  gt() %>%
  tab_header(title = "Effect of More Tweets on High Quality Polls") %>%
  tab_spanner(label = "Data from fivethirtyeight and Trump Tweet Archive", columns = 
                c("term", "estimate", "conf.low", "conf.high")) %>%
  cols_label(term = "Variable", estimate = "Estimate", conf.low =
               "Lower Bound", conf.high = "Upper Bound")


```

# 2D

```{r Question 2D, echo = FALSE}
formula <- -0.004344031 * 84 - 2.874972881 * 1 + 0.019158192 * 84 + 41.500711791 

# Derived the formula from the table and regression statistics above.

formula

regression_model_2c %>%
  augment(data = joined_polls) %>%
  filter(pollster == "Monmouth University", end_date == "2019-09-19") %>%
  slice(1) %>%
  pull(.fitted)

# I used questions on Piazza to figure out how to use augment for this and get
# the best estimate of the value. 

```

# 2E

I would interpret the coefficient with total tweets in this regression as the
impact the total tweets have on his approval rating and the estimated causal 
effect it has on Democrats' approval ratings. The actual coefficient would be
the estimated effect that one more tweet per week would have on the Democrats'
approval rating. This would also be the effect that the tweets have on his 
reported approval ratings. I would interpret the coefficient 
of approval as the causal effect that the reported approval ratings have on 
Democrats' approval ratings. In this case, the coefficient is the impact that
one more increase in the rating has on the Democrats' approval rating. Lastly, 
the coefficient regression for Democrats is the causal effect being assigned to
the high or low tweet volume has on Democrats' approval ratings. This is the
average causal effect that a high or low tweet volume has on the approval rates
on Democrats as it is randomly assigned and looks directly at the changes in
approval rating associated with Trump's week's assigned treatment 
(high or low tweet volume).

# 3

```{r Question 3, echo=FALSE}
joined_polls$month <- ceiling(poll$week/4)

tweets$month <- ceiling(tweets$week/4)


joined_polls %>%
  mutate(high_q = ifelse(grade %in% c("A+", "A", "A-"), "A+, A- or A", "Lower than A- or Missing")) %>%
  group_by(month, high_q) %>%
  mutate(average = mean(approve)) %>%
  ggplot(aes(month, average, color = high_q)) +
  scale_color_manual(values = c("red", "blue")) +
  theme_classic() +
  labs(title = "Approval Rating By Poll Quality",
       x = "Month", y = "Average Approval Rating",
       color = "Poll Quality") +
  geom_line()

# I was able to derive most of this on my own but had immense trouble with 
# Poll Quality which Naina Tejani helped me with. She is the one who helped
# me with mutate and walked me through it.

tweets_month <- tweets %>%
  filter(month <= 11) %>%
  group_by(month) 

ggplot(tweets_month, aes(month)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Month",
       y = "Tweets",
       title = "Total Tweets",
       subtitle = "President Trump")

# This plot was pretyy straightforward, and I did not have much difficulty 
# creating this.

# I was unable to make the final two graphs as I was having an error with getting 
# approve, and unfortunately, I could not get it to work in time.

# question_33 <- joined_polls %>%
#  group_by(month) %>%
#  nest()

# question_33 %>%
#  mutate(mod = map(poll, ~lm(approve ~ total_tweets + high_q, data = .)), 
#         reg_results = map(mod, ~ tidy(., conf.int = TRUE)),
#         coef = map_dbl(reg_results, ~filter(., term == "high_q") %>%
#         pull(estimate)), se = map_dbl(reg_results, ~ filter(.,
#         term == "high_q") %>% pull(std.error)), upper = coef + 1.96 *
#           se, lower = coef - 1.96 * se) %>%
#        ggplot(aes(x = month, y = coef)) +
#        geom_hline(yintercept = 0, linetpe = "dashed") +
#        geom_errorbar(aes(ymin = lower, ymax = upper), color = "darkgreen") +
#        theme_classic() +
#        labs(title = "Effect of Total Tweets \n on Estimated Approval Rating",
#        subtitle = "Controlling for Poll Quality",
#        x = "Month", y = "Coefficient")
  

```

Collaborators: Tahmid Ahmed, Jun Yong Kim, Naina Tejani, Hamid Khan