---
title: "pset_2.Rmd"
author: "Hamaad Mehal"
date: "2/12/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(devtools)
library(tidyverse)
library(fivethirtyeight)

# this chunk loads all the necessary tools and data for the endoresement info.
# Initially, I forgot to install fivethirtyeight in the console which presented
# issues, but Asmer Safi helped me with this.

```

```{r}
first_endorsement <- endorsements_2020 %>%
  arrange(date) %>%
  slice(1) %>%
  pull(date)

# This pulls the first endorsement date from the data by arranging it by 
# first and then pulling the first data point from the endorsements. I ran
# into an issue because I initially grouped by candidate but quickly realized
# that was unnecessary. Yao Yu assisted me with debugging the slice function 
# here.

```
The earliest date for an endorsement in the dataset is `r first_endorsement`.

```{r}
recent_endorsement <- endorsements_2020 %>%
  arrange(desc(date)) %>%
  slice(1) %>%
  pull(date)

# This pulls the most recent endorsement date from the data by arranging it by 
# most recent and then pulling the first data point (most recent) from the 
# endorsements. I went through the same process on this as the one before. 

```
The most recent date for an endorsement is `r recent_endorsement`.
```{r}
mayor_endorsement <- endorsements_2020 %>%
  filter(endorsements_2020$position == "mayor", 
         endorsements_2020$endorsee == "Pete Buttigieg") %>%
  select(endorser) %>%
  pull(endorser)

# I filtered through the data by looking at endorsers who were mayors and
# seeing which one of these mayoral endorsers endorsed Buttigieg. My thought 
# process was fairly straightforward on this topic as I remembered filtering
# similarly in datacamp.

```
`r mayor_endorsement` is the mayor that has endorsed Pete Buttigieg.

```{r}
NH_endorsement <- endorsements_2020 %>%
  filter(endorsements_2020$state == "NH") %>%
  summarize(mean = mean(points)) %>%
  pull(mean)

# I filtered for only New Hampshire data points and then took the average for 
# the points from New Hampshire by summing it and averaging it using mean. My
# thought process on this was also fairly straightforward as I recently did this
# in Datacamp too.

```
Endorsers from New Hampshire have an average of `r NH_endorsement` endorsement 
points.

```{r}
femalecandidate_endorsement <- endorsements_2020 %>%
  filter(endorsee %in% c("Elizabeth Warren", "Amy Klobuchar")) %>%
  summarize(sum = sum(points)) %>%
  pull(sum)

# Elias assisted with code by reminding me of %in%.
# I filtered for specifically Warren and Klobuchar first. Then just summed up
# the total points for those two candidates to get the result. Initially, I 
# experienced trouble due to the fact that I did not remember how to filter for
# two sets of characters.

```
Between them, the two female candidates who remain in the race (Amy Klobuchar 
and Elizabeth Warren) have a total of `r femalecandidate_endorsement` 
endorsement points.



```{r}
  position <- class(endorsements_2020$position) 

# I took the class of the position row. You helped me how to print the class() 
# function as I was previously unfamiliar with it.

```
The variable "position" is a `r position` class of variable.

```{r}
  endorser <- class(endorsements_2020$endorser)

# I took the class of the endorser row. I figured out how to do this from the
# same process of the previous chunk.

```
The variable "endorser" is a `r endorser` class of variable.


```{r}
  points <- class(endorsements_2020$points)

# I took the class of the points row. A similar process occurred with this as 
# with the preceding two chunks.

```
The variable "points" is a `r points` class of variable.

```{r}
library(ggplot2)
library(gov.1005.data)
library(ggthemes)

# I loaded the library with necessary data (gov.1005.data) and the gg tools
# to create a graph as I remember doing this in class. 

```

```{r}
ages <- congress%>%
filter(party %in% c("R", "D")) %>%
group_by(year, party) %>%
summarize(avgAge=mean(age))

ggplot(ages, aes(year,avgAge, color=party))+
  geom_line() +
  annotate("text", x = 1965, y = 56, label = "Republicans", color = "red") +
  annotate("text", x = 2000, y = 58, label = "Democrats", color = "blue") +
  scale_x_continuous(limits = c(1947,2013), breaks = c(1950, 1960, 1970, 
  1980, 1990, 2000, 2010),label = c("1950", "'60", "'70", "'80", "'90", "2000",
  "'10")) +
  scale_y_continuous(limits = c(40,62.5), breaks = c(40, 45, 50, 55, 60), 
  label = c("40", "45", "50", "55", "60")) +
  theme_fivethirtyeight() +
  theme(legend.position = "none") +
  labs(title = "Average Age of Members of Congress", 
       subtitle = "At start of term, 1947-2013", 
       caption = "Source: fivethirtyeight package") + 
  scale_color_manual(values = c("Blue", "Red"))

# I took the skeleton for this code from last Tuesday's code in class. 
# Using the hints on the PSET, I figured out how to use annotate(), scale, and,
# lab with the help of Ella Michaels, Prabidhik KC, and Yao Yu. This took a lot of
# copy/pasting, as well as trial-and-error, to figure out how to actually use 
# these new functions. I figured out how to adjust the color and Democrat 
#line with the help of Asmer.

```
